oREV item selection

### 2022-11-19 analysis/item_selection.Rmd
add item selectio pareto k

```{r setup, include=FALSE}
library(tidyverse)
library(ggpubr)
library(ggthemes)
library(tidybayes)

@@

@@

```{r}
easiness_rasch <- eta_rasch %>% pull(Estimate.eta_Intercept)
infit <- rasch_fit_mode %>% filter(fit_index == "infit")%>%pull(mode)
outfit <- rasch_fit_mode %>% filter(fit_index == "outfit")%>%pull(mode)
disc_2PL <- coef_irt3$targetWord[, , "logalpha_Intercept"] %>% as_tibble(rownames = "item")%>%pull(Estimate)
```

@@

  #mean_pkd <- mean(pkd[subset])/2

	# sel <- items[subset == TRUE]
	# 
	# sub_dat <- data%>%
	#   filter(targetWord %in% sel)%>%
	#   group_by(subjID)%>%
	#   summarise(mean_sub = mean(correct))
	# 
	# cor <- cor(sub_dat$mean_sub,full$mean_full)
	# 
	# return(spacing + mean_discrim/6 + cor/3)
	return(spacing + mean_infit + mean_outfit+ var_disc_2PL )
}

@@

simulated_annealing_rasch <- function(k, cooling_ratio=0.999, reset_thresh=1000, break_thresh=10000) {
  easiness_rasch <- eta_rasch %>% pull(Estimate.eta_Intercept)
  infit <- rasch_fit_mode %>% filter(fit_index == "infit")%>%pull(mode)
  #infit <- maxi%>%pull(infit)
  outfit <- rasch_fit_mode %>% filter(fit_index == "outfit")%>%pull(mode)
  #outfit <- maxi%>%pull(outfit)
  #pkd <- maxi%>%arrange(targetWord)%>%pull(influence_pareto_k)
  N <- length(easiness)

@@

```{r, warning=FALSE}
sim_size_rasch <- tibble()

for (i in 5:6) {

  sim_size_rasch <- bind_rows(sim_size_rasch, row)
}

saveRDS(sim_size_rasch, "../saves/sim_size_rasch.rds")

sim_size_rasch%>%
  group_by(size)%>%
  summarise(mean_cor = mean(cor),
         min = min(cor),
         max = max(cor))%>%
  ggplot(aes(x = factor(size), y = mean_cor))+
  geom_pointrange(aes(ymin=min, max = max), pch = 1)+
  geom_line(aes(group = 1))+
  scale_linetype(name = "Run")+
  theme_minimal()+
  labs(x = "No. of items", y = "Correlation with full test")

@@

irt_comp_size%>%
  pivot_longer(cols = c(model_comparison_ratio, correlation), names_to = "type",values_to = "value")%>% 
  ggplot(aes(x = factor(size), y = value))+
  geom_point(pch = 1)+
  geom_line()+
  facet_grid(type~. , scales = "free_y")+
  theme_bw()+
  labs(x = "No. of items", y = "Comparison value")
```

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(ggpubr)
library(ggthemes)
library(tidybayes)
library(brms)
library(rstan)
library(loo)
library(coda)

@@

## Fit model

```{r}
prior_1pl_guess <- prior("normal(0, 2)", class = "b", nlpar = "eta") +
  prior("normal(0, 1)", class = "sd", group = "subjID", nlpar = "eta") +
  prior("normal(0, 3)", class = "sd", group = "targetWord", nlpar = "eta")

irt1_guess_standata <- brms:::make_standata(
  formula = bf(
    correct ~ 0.25 + 0.75 * inv_logit(eta),
    eta ~ 1 + (1 | targetWord) + (1 | subjID),
    nl = TRUE
  ),
  data = irt_dat,
  family = brmsfamily("bernoulli", "identity"),
  prior = prior_1pl_guess
)

irt1_guess_itemloo <- stan(
  file = "../analysis/irt1_guess_itemloo.stan",
  data = irt1_guess_standata[c("N", "Y", "N_1", "J_1", "N_2", "J_2")],
  control = list(adapt_delta = 0.95, max_treedepth = 12),
  cores = 6,
  chains = 6,
  iter = 6000
)
saveRDS(irt1_guess_itemloo, "../saves/irt1_guess_itemloo.rds")

irt1_guess_itemloo_loom <- loo(irt1_guess_itemloo, pars = "loglik_m")

saveRDS(irt1_guess_itemloo_loom, file = "../saves/irt1_guess_looitems_loom.rds")

irt1_guess_itemloo_idxs <- irt_dat %>%
  mutate(item_id = as.integer(factor(targetWord))) %>%
  group_by(targetWord) %>%
  summarize(
    mean_correct = mean(correct),
    item_id = unique(item_id),
    targetWord = unique(targetWord)
  ) %>%
  full_join(mutate(as_tibble(irt1_guess_itemloo_loom$pointwise[, "influence_pareto_k", drop = FALSE]), item_id = row_number())) %>%
  rename(pareto_k = influence_pareto_k) %>%
  full_join(
    as_draws_df(irt1_guess_itemloo) %>% 
      select(.chain, .iteration, starts_with("infit"), starts_with("outfit"), starts_with("r_2")) %>% 
      pivot_longer(-c(.chain, .iteration), names_pattern = "(.+)\\[([0-9]+)\\]", names_to = c(".value", "item_id")) %>% 
      rename(threshold = r_2_eta_1) %>% 
      mutate(item_id = as.integer(item_id)) %>% 
      group_by(item_id) %>% 
      summarize(across(c(infit, outfit, threshold), list(mean = mean, mode = estimate_mode, hdi_lower = hdi_lower, hdi_upper = hdi_upper)))
  ) %>%
  arrange(pareto_k) %>%
  print(n = nrow(.))
saveRDS(irt1_guess_itemloo_idxs, file = "../saves/irt1_guess_itemloo_idxs.rds")
```

@@

```{r}
# easiness_rasch <- eta_rasch %>% pull(Estimate.eta_Intercept)
# infit <- rasch_fit_mode %>% filter(fit_index == "infit")%>%pull(mode)
# outfit <- rasch_fit_mode %>% filter(fit_index == "outfit")%>%pull(mode)
# disc_2PL <- coef_irt3$targetWord[, , "logalpha_Intercept"] %>% as_tibble(rownames = "item")%>%pull(Estimate)

easiness_rasch <- irt1_guess_itemloo_idxs %>% arrange(targetWord)%>%pull(threshold_mode)
infit <- irt1_guess_itemloo_idxs %>% arrange(targetWord)%>% pull(infit_mode)
outfit <- irt1_guess_itemloo_idxs%>% arrange(targetWord) %>% pull(outfit_mode)
disc_2PL <- coef_irt3$targetWord[, , "logalpha_Intercept"] %>% as_tibble(rownames = "item")%>%pull(Estimate)
```

@@

  mean_pkd <- mean(pkd[subset])/4

	# sel <- items[subset == TRUE]
	# 
	# sub_dat <- data%>%
	#   filter(targetWord %in% sel)%>%
	#   group_by(subjID)%>%
	#   summarise(mean_sub = mean(correct))
	# 
	# cor <- cor(sub_dat$mean_sub,full$mean_full)
	# 
	# return(spacing + mean_discrim/6 + cor/3)
	return(spacing + mean_infit + mean_outfit+ var_disc_2PL +mean_pkd)
}

@@

simulated_annealing_rasch <- function(k, cooling_ratio=0.999, reset_thresh=1000, break_thresh=10000) {

  easiness <- irt1_guess_itemloo_idxs %>% arrange(targetWord)%>%pull(threshold_mode)
  infit <- irt1_guess_itemloo_idxs %>% arrange(targetWord)%>% pull(infit_mode)
  outfit <- irt1_guess_itemloo_idxs%>% arrange(targetWord) %>% pull(outfit_mode)
  disc_2PL <- coef_irt3$targetWord[, , "logalpha_Intercept"] %>% as_tibble(rownames = "item")%>%pull(Estimate)
  pkd <- irt1_guess_itemloo_idxs%>% arrange(targetWord) %>% pull(pareto_k)

  #easiness_rasch <- eta_rasch %>% pull(Estimate.eta_Intercept)
  #infit <- rasch_fit_mode %>% filter(fit_index == "infit")%>%pull(mode)
  #infit <- maxi%>%pull(infit)
  #outfit <- rasch_fit_mode %>% filter(fit_index == "outfit")%>%pull(mode)
  #outfit <- maxi%>%pull(outfit)
  #pkd <- maxi%>%arrange(targetWord)%>%pull(influence_pareto_k)
  N <- length(easiness_rasch)

@@

@@

irt_comp_size%>%
  pivot_longer(cols = c(ratio, correlation), names_to = "type",values_to = "value")%>% 
  ggplot(aes(x = factor(size), y = value))+
  geom_point(pch = 1)+
  geom_line()+
  facet_grid(type~. , scales = "free_y")+
  theme_bw()+
  labs(x = "No. of items", y = "Comparison value")
```
